Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2020-08-06 bbbq_article.tex
Show figure
Update names

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1/fig_bbbq_1.png}
  \caption{
    Percentage of MHC-I epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
    \richel{
      the data underlying this figure has been simulated
    }
  }
  \label{fig:1}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_2/fig_bbbq_2.png}
  \caption{
    \% epitopes overlapping with transmembrane helix
    for a human, COVID-19 and Mycobacterium proteome.
    \richel{
      the data underlying this figure has been simulated
    }
  }
  \label{fig:2}
\end{figure}

@@

@@

>>>>

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1/fig_f_tmh_mhc1.png}
  \caption{
    Percentage of MHC-I epitopes overlapping with TMHs
    for a human, viral and bacterial proteome.
  }
  \label{fig:1}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1/fig_f_tmh_mhc2.png}
  \caption{
    \% epitopes overlapping with transmembrane helix
    for a human, COVID-19 and Mycobacterium proteome.
  }
  \label{fig:2}
\end{figure}

@@

\begin{figure}[!htbp]
  \includegraphics[width=\textwidth]{bbbq_1/fig_ic50_distribution.png}
  \caption{
    Distribution of IC50 estimations per haplotype per target.
    The IC50 value is plotted on a logarithmic scale.
  }
  \label{fig:1}
\end{figure}

@@

\input{bbbq_1/table_ic50_binders.latex}
